---
author: Apoorva Lal
title: "Paper Title"
subtitle: "Subtitle"
date: "2018-06-08"
institute: 'Stanford University'
output:
  beamer_presentation:
    keep_tex: true
    # theme: Berlin
    colortheme: "dolphin"
    theme: metropolis
    slide_level: 2
    incremental: no
    toc: true
    fig_width: 5
    fig_height: 2.5
classoption: "compress,aspectratio=169"
fontsize: 11pt
bibliography: /home/alal/Dropbox/MyLibrary.bib
header-includes:
  - \usepackage[english]{babel}
  - \usepackage{setspace,booktabs, bbm}
  - \DeclareUnicodeCharacter{2010}{-}
  - \usepackage[sfdefault,scaled=.85]{FiraSans}
  - \setbeamerfont{section in head/foot}{size=\tiny}
  - \usepackage{bookmark}
  - \hypersetup{bookmarksdepth=4,bookmarksnumbered=true,bookmarksopen=true}
  - \usepackage{/home/alal/Templates/boilerplate/lal_default_beamer}
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.path='Figs/', cache=T,
                      echo=FALSE, warning=FALSE, message=FALSE)
```

```{r, include=F}
####################################################
rm(list=ls())
if (require('LalRUtils')==F) {
    library(devtools)
    devtools::install_github("apoorvalal/LalRUtils")
}
load_or_install(c('tidyverse','magrittr','Hmisc','knitr','data.table',
  'lfe','sf','tmap','viridis'))
sessionInfo()
theme_set(theme_bw())
```

# A Section Header

## A Slide Header

### A Subtitle

- Point A
- Point B
- Point C

## Multicolumn Slide

\begin{columns}
\begin{column}{0.6\textwidth}
\begin{itemize}
   \item some text here some text here some text here some text here some text here
   \item another point
\end{itemize}
\end{column}
\begin{column}{0.4\textwidth}
    \begin{center}
    Picture goes here
     % \includegraphics[width=1\textwidth]{picture.png}
     \end{center}
\end{column}
\end{columns}

## Graphs

```{r, fig.cap="Figure Caption", fig.align='center'}

library(ggplot2)
p = ggplot(diamonds, aes(depth, colour = cut)) +
  geom_density() +
  xlim(55, 70)
p
```
_ _ _

\LARGE Breakout page

# Using LaTeX Parts: Equations

## Linear Model

$$
\hat{\beta} = \text{argmin}_{b \in \mathbb{R}} S(b) = \left(
\frac{1}{n} \sum_{i=1}^n x_i x_i^T \right)^{-1} \cdot \frac{1}{n}
\sum_{i=1}^n x_i y_i
$$
or in matrix form

$$ \hat{\beta} = (X^TX)^{-1} X^T y $$


## Using LaTeX Parts: Blocks

As one example of falling back into \LaTeX, consider the example of
three different block environments are pre-defined and may be styled
with an optional background color.

<!-- this sets the background -->

\begin{block}{Default}
  Block content.
\end{block}

\begin{alertblock}{Alert}
  Block content.
\end{alertblock}

\begin{exampleblock}{Example}
  Block content.
\end{exampleblock}

# Section 3

## Subsection 3
