---
title: "Handy Universal Note Template"
author: "Apoorva Lal"
date: "`r Sys.Date()`"
numbersections: true
# output: tint::tintPdf
output: tint::tintHtml
bibliography: /home/alal/Dropbox/theoryPapers.bib
link-citations: yes
---

```{r setup, include=FALSE}
rm(list = ls())
library(LalRUtils)
libreq(data.table, magrittr, tidyverse, janitor, stargazer2, knitr)
set.seed(42)
library(tint)
library(ggplot2)
theme_set(theme_minimal())

knitr::opts_chunk$set(
  echo    = F,          # don't show code
  include = T,          # show output
  message = F,          # don't show messages (less serious warnings)
  cache   = T
)

mtcars$am <- factor(mtcars$am, labels=c("manual", "automatic"))
```

# Intro

Some text here. cite something [@dessein2002authority]

another cite [@fearon1994domestic]

Basic maths

\begin{align*}
y_i & = x_i' \beta + \epsilon_i \\
\epsilon_i & \sim \mathcal{N}(0, \sigma^2)
\end{align*}



# Included Code

```{r random-draw, echo = TRUE}

epsilon = rnorm(100, 0, 1)

epsilon %>% head

```


# Margin Examples

The margin can be used for arbirtrary 'figure' environments by using
the `knitr` option `marginfigure` along with standard \LaTeX
mathematical markup.

```{marginfigure, echo = T}
We know from _the first fundamental theorem of calculus_ that for $x$
in $[a, b]$: $$\frac{d}{dx}\left( \int_{a}^{x} f(u)\,du\right)=f(x).$$
```

We can also add a 'note' using the standard `pandoc` notation of text
in square brackets following an hat symbol: `^[text here]`.^[This is a
sidenote that was entered using a footnote.]

here^[another numbered note]

Notes can also be added in-line using an R command and the
`margin_note()` function. `r margin_note("Some text.")` Note that this
note is unnumbered.


# Margin Figures


```{r fig-nocap-margin-second, fig.margin=TRUE, fig.width=4, fig.height=4}

ggplot(mtcars, aes(wt, mpg)) + geom_point(size=3,
    aes(colour=factor(cyl))) + theme_tint() +
    theme(legend.position="none") + ggtitle("Margin Figure")
```


# Full Width Figures

Figures can span across the entire page; this is enabled by using the
chunk option `fig.fullwidth = TRUE`. Using the default them but
conditioning by number of cylinders:

```{r fig-fullwidth, fig.width = 10, fig.height = 3, fig.fullwidth = TRUE, fig.cap = "A full width figure."}

ggplot(mtcars, aes(wt, mpg)) + geom_point(size=3, aes(colour=am)) +
    facet_wrap(~ factor(cyl)) + theme(legend.position="bottom") +
    ggtitle("Full Width Figure")
```

# Main Column Figures

Besides margin and full width figures, one can of course also include
figures constrained to the main column. This is the default type of
figures in the LaTeX/HTML output. A single figure with cylinders in
color and transmission not controlled for, and once again using
`theme_tint()`:

```{r fig-main, fig.cap = "A figure in the main column."}
ggplot(mtcars, aes(wt, mpg)) +
    geom_point(size=2, aes(colour=factor(cyl))) +
    theme_tint() + theme(legend.position="none") +
    ggtitle("Main Column Figure")
```


<!--
As [knitr](https://github.com/yihui/knitr) \citep{cran:knitr} is
driving the conversion, many of its options also apply.  See the
documentation for the [tufte](https://github.com/rstudio/tufte) and
[knitr](https://github.com/yihui/knitr) for details.

Full documentation is available in the [longer PDF
vignette](https://eddelbuettel.github.io/tint/tintPDF.pdf), its
[Lato](https://eddelbuettel.github.io/tint/tintPDFLato.pdf) and
[Garamond](https://eddelbuettel.github.io/tint/tintPDFGaramond.pdf)
variants (see below) as well as the [longer HTML
vignette](https://eddelbuettel.github.io/tint/tintHTML.html). -->


