---
title: Title
author: Apoorva Lal
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    theme: spacelab
    highlight: tango
    code_folding: hide
    toc: true
    toc_float: false
    toc_depth: 3
    fig_width:  10
    fig_height: 8
---


<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
}
</style>

```{r}
options(digits=2)
rm(list=ls())
library(LalRUtils)

load_or_install(c('tidyverse', 'magrittr', 'data.table', 'knitr',
  'stargazer','lfe','rio', 'gridExtra', 'kableExtra'))

theme_set(lal_plot_theme())

knitr::opts_knit$set( echo=TRUE, warning=FALSE, message=FALSE, cache=FALSE )
knitr::opts_chunk$set( echo=TRUE, warning=FALSE, message=FALSE, cache=FALSE )
```

The quick brown fox jumped over the lazy dog^[but the dog's laziness
is heavily debated].

\begin{align*}
\max_{c_t,k_{t+1}} &  \sum_{t=1}^{\infty} \beta^t u(c_t)  \\
  s.t. & \enspace c_{t} + k_{t+1} \leq f(k_t) + (1-\delta)k_t
\end{align*}

# Estimation Framework

\begin{align*}
\text{outcome}_{ict} = \alpha_i & + \sum_{k=0}^2 \beta_{t-k}^p
PPI_{ict-k} + \gamma_{ct} + \epsilon_{ict} \\
\text{outcome}_{ict} = \alpha_i & + \sum_{k=0}^2 \beta_{t-k}^p PPI_{ict-k} +
\sum_{k=0}^2 + \beta_{t-k}^m CPI_{ict-k} + \\ & \gamma_{c}\times
trend_t + \epsilon_{ict}
\end{align*}

# Regression output

```{r}
lm1 = felm(hwy ~ cyl ,   data = mpg)
lm2 = (felm(hwy ~ cyl | factor(trans)| 0 | manufacturer, data=mpg))
```

```{r, results='asis'}
#%%
stargazer(lm1, lm2, type='html')
#%%
```

# Figures

```{r, fig.margin=T}
#%%
library(ggplot2)
mtcars2 <- mtcars
mtcars2$am <- factor(
  mtcars$am, labels = c('automatic', 'manual')
)
ggplot(mtcars2, aes(hp, mpg, color = am)) +
  geom_point() + geom_smooth() +
  theme(legend.position = 'bottom')
#%%
```

# Bibliography
