---
title: Document Title
author: Apoorva Lal
date: "`r format(Sys.time(), '%B %d, %Y')`"
bibliography: /home/alal/Dropbox/MyLibrary.bib
csl: econometrica.csl
output:
  html_document:
    theme: flatly
    # theme: paper
    # theme: cosmo
    toc: true
    toc_float: true
    toc_depth: 2
    code_folding: hide
---

# 1. Preliminaries

**started off as Chapter-by-chapter notes for
@AngristMostlyharmlesseconometrics2008b**; based on material from
[Josh Gottlieb](http://www.joshuagottlieb.ca/)'s research design class
with additional material from
@CameronMicroeconometricsmethodsapplications2005

```{r,include=F}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      echo=TRUE, warning=FALSE, message=FALSE,
                      cache=TRUE
)

options(digits=2)
# R Imports Boilerplate
rm(list=ls())
user_name = Sys.info()['user']
temp_path = Sys.getenv()['TMP']
load_or_install(c('tidyverse','data.table', 'stargazer','lfe','rio'))
theme_set(theme_minimal())
```

## Cite

@DeatonPaneldatatime1985

The quick brown fox jumped over the lazy dog^[but the dog's laziness
is heavily debated].

\begin{align*}
\max_{c_t,k_{t+1}} &  \sum_{t=1}^{\infty} \beta^t u(c_t)  \\
  s.t. & \enspace c_{t} + k_{t+1} \leq f(k_t) + (1-\delta)k_t
\end{align*}

# Estimation Framework

\begin{align*}
\text{outcome}_{ict} = \alpha_i & + \sum_{k=0}^2 \beta_{t-k}^p
PPI_{ict-k} + \gamma_{ct} + \epsilon_{ict} \\
\text{outcome}_{ict} = \alpha_i & + \sum_{k=0}^2 \beta_{t-k}^p PPI_{ict-k} +
\sum_{k=0}^2 + \beta_{t-k}^m CPI_{ict-k} + \\ & \gamma_{c}\times
trend_t + \epsilon_{ict}
\end{align*}


# Regression output

```{r}
lm1 = felm(hwy ~ cyl ,   data = mpg)
lm2 = (felm(hwy ~ cyl | factor(trans)| 0 | manufacturer, data=mpg))
```

```{r, results='asis'}
#%%
stargazer(lm1, lm2, type='html')
#%%
```

# Figures

```{r, fig.margin=T}
#%%
library(ggplot2)
mtcars2 <- mtcars
mtcars2$am <- factor(
  mtcars$am, labels = c('automatic', 'manual')
)
ggplot(mtcars2, aes(hp, mpg, color = am)) +
  geom_point() + geom_smooth() +
  theme(legend.position = 'bottom')
#%%
```

# Bibliography
