---
title: "Lecture 1: Introduction"
subtitle: "subtitle here"
author: Apoorva Lal | Stanford
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts]
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

<!--- For HTML renders - selection from math_shortcuts.tex --->
`r if (!knitr:::is_latex_output()) '
$\\DeclareMathOperator*{\\argmin}{argmin}$
$\\newcommand{\\var}{\\mathrm{Var}}$
$\\newcommand{\\epsi}{\\varepsilon}$
$\\newcommand{\\phii}{\\varphi}$
$\\newcommand\\Bigpar[1]{\\left( #1 \\right )}$
$\\newcommand\\Bigbr[1]{\\left[ #1 \\right ]}$
$\\newcommand\\Bigcr[1]{\\left\\{ #1 \\right \\}}$
$\\newcommand\\SetB[1]{\\left\\{ #1 \\right\\}}$
$\\newcommand\\Sett[1]{\\mathcal{#1}}$
$\\newcommand{\\Data}{\\mathcal{D}}$
$\\newcommand{\\Ubr}[2]{\\underbrace{#1}_{\\text{#2}}}$
$\\newcommand{\\Obr}[2]{ \\overbrace{#1}^{\\text{#2}}}$
$\\newcommand{\\sumiN}{\\ensuremath{\\sum_{i=1}^N}}$
$\\newcommand{\\dydx}[2]{\\frac{\\partial #1}{\\partial #2}}$
$\\newcommand\\Indic[1]{\\mathds{1}_{#1}}$
$\\newcommand{\\Realm}[1]{\\mathbb{R}^{#1}}$
$\\newcommand{\\Exp}[1]{\\mathbb{E}\\left[#1\\right]}$
$\\newcommand{\\Expt}[2]{\\mathbb{E}_{#1}\\left[#2\\right]}$
$\\newcommand{\\Var}[1]{\\mathbb{V}\\left[#1\\right]}$
$\\newcommand{\\Covar}[1]{\\text{Cov}\\left[#1\\right]}$
$\\newcommand{\\Prob}[1]{\\mathbf{Pr}\\left(#1\\right)}$
$\\newcommand{\\Supp}[1]{\\text{Supp}\\left[#1\\right]}$
$\\newcommand{\\doyx}{\\Prob{Y \\, |\\,\\mathsf{do} (X = x)}}$
$\\newcommand{\\doo}[1]{\\Prob{Y |\\,\\mathsf{do} (#1) }}$
$\\newcommand{\\R}{\\ensuremath{\\mathbb{R}}}$
$\\newcommand{\\Z}{\\ensuremath{\\mathbb{Z}}}$
$\\newcommand{\\wh}[1]{\\widehat{#1}} % Wide hat$
$\\newcommand{\\wt}[1]{\\widetilde{#1}} % Wide tilde$
$\\newcommand{\\wb}[1]{\\overline{#1}} % Wide bar$
$\\newcommand\\Ol[1]{\\overline{#1}}$
$\\newcommand\\Ul[1]{\\underline{#1}}$
$\\newcommand\\Str[1]{#1^{*}}$
$\\newcommand{\\F}{\\mathsf{F}}$
$\\newcommand{\\ff}{\\mathsf{f}}$
$\\newcommand{\\Cdf}[1]{\\mathbb{F}\\left(#1\\right)}$
$\\newcommand{\\Cdff}[2]{\\mathbb{F}_{#1}\\left(#2\\right)}$
$\\newcommand{\\Pdf}[1]{\\mathsf{f}\\left(#1\\right)}$
$\\newcommand{\\Pdff}[2]{\\mathsf{f}_{#1}\\left(#2\\right)}$
$\\newcommand{\\dd}{\\mathsf{d}}$
$\\newcommand\\Normal[1]{\\mathcal{N} \\left( #1 \\right )}$
$\\newcommand\\Unif[1]{\\mathsf{U} \\left[ #1 \\right ]}$
$\\newcommand\\Bern[1]{\\mathsf{Bernoulli} \\left( #1 \\right )}$
$\\newcommand\\Binom[1]{\\mathsf{Bin} \\left( #1 \\right )}$
$\\newcommand\\Pois[1]{\\mathsf{Poi} \\left( #1 \\right )}$
$\\newcommand\\BetaD[1]{\\mathsf{Beta} \\left( #1 \\right )}$
$\\newcommand\\Diri[1]{\\mathsf{Dir} \\left( #1 \\right )}$
$\\newcommand\\Gdist[1]{\\mathsf{Gamma} \\left( #1 \\right )}$
$\\def\\mbf#1{\\mathbf{#1}}$
$\\def\\mrm#1{\\mathrm{#1}}$
$\\def\\mbi#1{\\boldsymbol{#1}}$
$\\def\\ve#1{\\mbi{#1}} % Vector notation$
$\\def\\vee#1{\\mathbf{#1}} % Vector notation$
$\\newcommand{\\Mat}[1]{\\mathbf{#1}}$
$\\newcommand{\\eucN}[1]{\\norm{#1}}$
$\\newcommand{\\lzero}[1]{\\norm{#1}_0}$
$\\newcommand{\\lone}[1]{\\norm{#1}_1}$
$\\newcommand{\\ltwo}[1]{\\norm{#1}_2}$
$\\newcommand{\\pnorm}[1]{\\norm{#1}_p}$
'`

```{r setup, include=FALSE}
# %% ####################################################
rm(list = ls())
library(LalRUtils)
LalRUtils::libreq(tidyverse, data.table, stargazer2, lfe, rio, foreach,
  magrittr, janitor, knitr, gapminder)
theme_set(lal_plot_theme())
options(repr.plot.width=12, repr.plot.height=9)
set.seed(42)
# %% ####################################################

options(htmltools.dir.version = FALSE)
opts_chunk$set(
  fig.align="center", fig.height=6, fig.width=10, dpi=300,
  cache=T, echo=F, warning=F, message=F
  )

theme_set(lal_plot_theme())
set.seed(42)
```

# Table of contents

1. [Sec1](#prologue)

2. [Sec2](#syllabus)


---
class: inverse, center, middle
name: prologue

# Prologue

<html><div style='float:left'></div><hr color='#EB811B' size=1px width=796px></html>

---

# Survey

Results from our [survey](https://goo.gl/forms/PjojERKMOpbo78JJ3)...

---
class: inverse, center, middle
name: syllabus

# Syllabus highlights

<html><div style='float:left'></div><hr color='#EB811B' size=1px width=796px></html>

(Read the full document [here](https://github.com/uo-ec607/syllabus/blob/master/syllabus.pdf).)

---

# ggplot2

```{r gapm_plot, dev="svg"}
ggplot(data = gapminder, mapping = aes(x = gdpPercap, y = lifeExp)) +
  geom_point()
```
